Section_8_Team1_Lab2_Report

### 2021-08-05 notebooks/Draft_Report.Rmd
updated text

Do COVID infection rates impact vacation travel distance for U.S. residents in the state of Texas? 
How does income, population density, and covid regulations in each county impact traveling?

@@

-->Need to explain distance of travel with

@@

```{r EDA, echo=FALSE, message=FALSE}
#Example Table
df$rural_cat <- ifelse(df$is_rural == 1, "Rural", "Urban")
table1::label(df$density) <- "County Population Density"
table1::label(df$cases) <- "County Covid-19 Cases"
table1::label(df$unemp_rate) <- "County Unemployment Rate"
table1::label(df$median_income) <- "County Median Income ($)"
table1::label(df$pct_lt17) <- "County Age < 17 years (%)"
table1::label(df$pct_gt65) <- "County Age > 65 years (%)"
# table1::label(df$is_rural) <- "County Type"
table1::table1(~density + cases + unemp_rate + median_income + pct_lt17 + pct_gt65 | rural_cat, data = df, caption = "Table 1: Texas County Variable Statistics", topclass="Rtable1-zebra", overall = "Total")

County <= as.factor(df$rural_cat)

df %>%
  mutate(
    cases = log(cases+1),
    deaths = log(deaths+1),
    long_trip = log(long_trip),
    density = log(density),
    median_income=log(median_income+1),
    unemp_rate = log(unemp_rate+1)
  ) %>%
  select(long_trip, cases, deaths, median_income, unemp_rate, density, pct_lt17, pct_gt65) %>%
  GGally::ggpairs(., 
               legend = 1,
               aes(color = County), 
               title = "Figure 1: Variable Characterstics",
               upper = list(continuous = wrap("cor", size = 2.5)),
               lower = list(continuous = wrap("points", alpha = 0.5, size=0.3)),
               diag = list(continuous = wrap("densityDiag", alpha = 0.5)),
               columnLabels=c("Distance", "Cases", "Deaths", "Income", "Unemployment", "Pop Density", "Age < 17","Age > 65"))+
               theme(legend.position = "bottom")

@@

$$
  Model 1 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income})
$$ 
$$
  Model 2 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income}) + \beta_4 h(\text{Unemployment Rate}) + \beta_5 h(\text{log(Population Density})
$$
$$
  Model 3 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income})
  + \beta_4 h(\text{Unemployment Rate}) + \beta_5 h(\text{log(Population Density}) + \beta_6 h(\text{log(% Age < 17}) + \beta_7 h(\text{log(% Age < 17})
$$

@@

Last, the significance of individual regression coefficients was tested using robust standard errors in R studio for model 3. The results are shown below: 
```{r coeftest}
#Run coeftest to show statistical significance of all variables in the model with robust standard errors
coeftest(model3, vcov = vcovHC(model3, type="HC1"))
```
From the t-test, we can see that Covid-19 cases and median income are statistically significant. Additionally, the percentage of adults greather than 65, the population density, and the Covid-19 death variables are even more statistically significant.

@@

##FINAL MODEL
par(mfrow = c(2, 2))
plot(model3, col="green") 
title("Model 3", line = -0.75, outer = TRUE)

>>>>

Do COVID-19 infection rates impact vacation travel distance for U.S. residents in the state of Texas? 
How does income, population density, and covid regulations in each county impact traveling?

@@

-->Need to explain distance of travel with bs TRANSPORT data
-->Need to add more to causal theory to justify variable selection

@@

```{r EDA, echo=FALSE, message=FALSE}
#Example Table
df$rural_cat <- ifelse(df$is_rural == 1, "Rural", "Urban")
table1::label(df$density) <- "County Population Density"
table1::label(df$cases) <- "County Covid-19 Cases"
table1::label(df$unemp_rate) <- "County Unemployment Rate"
table1::label(df$median_income) <- "County Median Income ($)"
table1::label(df$pct_lt17) <- "County Age < 17 years (%)"
table1::label(df$pct_gt65) <- "County Age > 65 years (%)"
# table1::label(df$is_rural) <- "County Type"
table1::table1(~density + cases + unemp_rate + median_income + pct_lt17 + pct_gt65 | rural_cat, data = df, caption = "Table 1: Texas County Variable Statistics", topclass="Rtable1-zebra", overall = "Total")
```
Below are histograms of variables that did not follow normal distribution and required transformation. Each of these variables was logarithmically transformed.
```{r scatterplots, message=FALSE}
attach(df)
par(mfrow=c(3,2))
hist(cases, main="Histogram of Covid-19 Cases")
hist(deaths, main="Histogram of Covid-19 Deaths")
hist(long_trip, main="Histogram of Distance")
hist(density, main="Histogram of Population Density")
hist(unemp_rate, main="Histogram of Unemployment Rate")
hist(median_income, main="Histogram of Median Income")

```{r ggally, echo=FALSE, message=FALSE}
County = as.factor(df$rural_cat)

# df %>%
#   mutate(
#     cases = log(cases+1),
#     deaths = log(deaths+1),
#     long_trip = log(long_trip),
#     density = log(density),
#     median_income=log(median_income+1),
#     unemp_rate = log(unemp_rate+1)
#   ) %>%
#   select(long_trip, cases, deaths, median_income, unemp_rate, density, pct_lt17, pct_gt65) %>%
#   GGally::ggpairs(.,
#                legend = 1,
#                aes(color = County),
#                title = "Figure 1: Variable Characterstics",
#                upper = list(continuous = wrap("cor", size = 2.5)),
#                lower = list(continuous = wrap("points", alpha = 0.5, size=0.3)),
#                diag = list(continuous = wrap("densityDiag", alpha = 0.5)),
#                columnLabels=c("Distance", "Cases", "Deaths", "Income", "Unemployment", "Pop Density", "Age < 17","Age > 65"))+
#                theme(legend.position = "bottom")

ggpairs(df, columns = 3:ncol(df), legend = 1, aes(color = County), title = "Figure 1: Variable Characterstics")
#                upper = list(continuous = wrap("cor", size = 2.5)),
#                lower = list(continuous = wrap("points", alpha = 0.5, size=0.3)),
#                diag = list(continuous = wrap("densityDiag", alpha = 0.5)))

@@

$$
  Model 1 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income})
$$

$$
  Model 2 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income}) + \beta_4 h(\text{Unemployment Rate}) + \beta_5 h(\text{log(Population Density})
$$

$$
  Model 3 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income})
  + \beta_4 h(\text{Unemployment Rate}) + \beta_5 h(\text{log(Population Density}) + \beta_6 h(\text{log(% Age < 17}) + \beta_7 h(\text{log(% Age < 17})
$$

@@

Last, the significance of individual regression coefficients was tested using robust standard errors in R studio for model 3. The results are shown below: 
```{r coeftest}
#Run coeftest to show statistical significance of all variables in the model with robust standard errors
coeftest(model2, vcov = vcovHC(model3, type="HC1"))
```
From the t-test, we can see that Covid-19 cases and median income are statistically significant. Additionally, the percentage of adults greather than 65, the population density, and the Covid-19 death variables are even more statistically significant.

@@

# Model 3
# par(mfrow = c(2, 2))
# plot(model3, col="green") 
# title("Model 3", line = -0.75, outer = TRUE)
